A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-22 FMCAD2021/8_appendix.tex
small changes
prop7 proof

Note that $\ell_{10}(n)$ is undefined for $n\le 0$ in $\paexp$. For convenience, we define $\ell_{10}(n)=0$ for $n\le 0$ in the following proof.

@@

\begin{proof}
By an induction on $n'$, we first show that for any $n' \in \Nat$, if $p \ge 2n'$, then $10^{n'} p \le 10^p$.

>>>>

Note that $\ell_{10}(n)$ is undefined for $n\le 0$ in $\paexp$. For convenience, we define for all $n\le 0$ that $\ell_{10}(n)=\ell_{10}(\max\{1,n\})=0$ in the following proof.

@@

\begin{proof}

First we show that for any $n' \in \Nat$, if $p \ge 2n'$, then $10^p \ge 10^{n'}10^{(p-n')}\ge 10^{n'}10(p-n')\ge 10^{n'}(5p+5(p-2n'))\ge  10^{n'}p$.
